---
editor_options: 
  markdown: 
    wrap: 72
---

## Ch.2 Computer Answer for questions 5, 10, and 11.

**C5** For the population of firms in the chemical industry, let rd
denote annual expenditures on research and development, and let sales
denote annual sales (both are in millions of dollars). 
(i) Write down a model (not an estimated equation) that implies a constant elasticity
between rd and sales. Which parameter is the elasticity?

```{r}
data('rdchem')
print('log(rd) = B0 + B1*log(sales) + u')
```

(ii) Now, estimate the model using the data in RDCHEM. Write out the
     estimated equation in the usual form. What is the estimated
     elasticity of rd with respect to sales? Explain in words what this
     elasticity means.

```{r}
model <- lm(log(rdchem$rd) ~ log(rdchem$sales), rdchem)
summary_model <- summary(model)
paste('The estimated elasticity is', round(model$coefficients[2],2))
print('This can be interpretted as \'An additional percent in sales, all else equal, will increase expenditures on R&D by 1.08%')
```

**C10** The data set in CATHOLIC includes test score information on over
7,000 students in the United States who were in eighth grade in 1988.
The variables math12 and read12 are scores on twelfth grade standardized math and reading tests, respectively. 
(i) How many students are in the sample? Find the means and standard deviations of math12 and
read12.

```{r}
paste(dim(catholic)[-2],'students.')
mean_math12 <- mean(catholic$math12)
mean_read12 <- mean(catholic$read12)
sd_math12 <- sd(catholic$math12)
sd_read12 <- sd(catholic$read12)

paste('Math12 Mean:',round(mean_math12,2))
paste('Math12 Standard Deviations:',round(sd_math12,2))
paste('Read12 Mean:',round(mean_read12,2))
paste('Read12 Standard Deviation:',round(sd_read12,2))
```

(ii) Run the simple regression of math12 on read12 to obtain the OLS
     intercept and slope estimates. Report the results in the form:

math12 = B0 + B1(read12) n = ?, R\^2 = ?

where you fill in the values for b\^ 0 and b\^ 1 and also replace the
question marks.

```{r}
model10 <- lm(catholic$math12 ~ catholic$read12, catholic)
summary(model10)
paste('R-Squared:',summary(model10)$r.squared)
paste('n = ',dim(catholic)[-2])
```

(iii) Does the intercept reported in part (ii) have a meaningful
      interpretation? Explain.

```{r}
paste('Yes, when the reading score is 0, we predict the math score to be 15.15 percent.')
```

(iv) Are you surprised by the b\^ 1 that you found? What about R2?

```{r}
paste('Slightly surprised by how much the intercept is. Also, half of the variation is math12 can be explained by read12 is pretty high.')
```

(v) Suppose that you present your findings to a superintendent of a
    school district, and the superintendent says, “Your findings show
    that to improve math scores we just need to improve reading scores,
    so we should hire more reading tutors.” How would you respond to
    this comment? (Hint: If you instead run the regression of read12 on
    math12, what would you expect to find?)

```{r}
model10_2 <- lm(catholic$read12 ~ catholic$math12, catholic)
summary(model10_2)
paste('We cannot establish a causal effect, so it wouldn\'t be wise to say one causes another to increase.')
```

**C11** Use the data in GPA1 to answer these questions. It is a sample
of Michigan State University undergraduates from the mid-1990s, and
includes current college GPA, colGPA, and a binary variable indicating
whether the student owned a personal computer (PC). 
(i) How many students are in the sample? Find the average and highest college GPAs.

```{r}
paste('n = ', dim(gpa1)[-2])
paste('Average GPA:',round(mean(gpa1$colGPA),2))
paste('Highest GPA:',max(gpa1$colGPA))
```

(ii) How many students owned their own PC?

```{r}
paste(length(gpa1$PC[gpa1$PC == 1]),'students owned computer.')
```

(iii) Estimate the simple regression equation colGPA= b0 + b1(PC) + u and
      report your estimates for b0 and b1. Interpret these estimates,
      including a discussion of the magnitudes.

```{r}
model11 <- lm(gpa1$colGPA ~ gpa1$PC, gpa1)
summary(model11)
paste('When a student doesn\'t own a PC, their GPA is',round(model11$coefficients[1],2))
paste('When a student owns a PC, their GPA is increased by',round(model11$coefficients[2],2))
```

(iv) What is the R-squared from the regression? What do you make of its
     magnitude?

```{r}
paste('R-Squared:',summary(model11)$r.squared)
print('Half of their GPA is attributed to whether or not they own their own PC.')
```

(v) Does your finding in part (iii) imply that owning a PC has a causal
    effect on colGPA? Explain.

```{r}
print('Although very interesting, it doesn\'t mean it is causal as it wasn\'t an experiment.')
```
